\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 implementation.tex
.

The presented technique was prototyped as a tool: PWA-Rel.
We compared it against S3CAM~\cite{zutshi2014multiple} on several academic
benchmarks.

@@

We used S3CAM to discover the abstraction graph $G$, which was then
filtered to remove the nodes from which error nodes were not
reachable. In our experiments we used $1$-relational modeling to
create the transition system from $G$. Using the BMC, we checked for
the given safety property. If a concrete trace was obtained, it was
further checked for reproducibility by sampling and simulating its `neighborhood' with the
$\simulate$ function. We define `neighborhood' as the abstract states
corresponding to the returned concrete trace. Specifically, $100$
samples were uniformly randomly chosen and simulated and tested for
error traces. This procedure can also be extended to obtaining
different discrete sequences or discrete trace sequences from the
model checker by requesting distinct counter-examples.

>>>>

The presented technique was prototyped as a tool: PWA-Rel.  We
compared it against S3CAM~\cite{zutshi2014multiple} on several
academic benchmarks. Below, we present the details of the
implementation and the benchmarks used.

@@

PWA-Rel uses S3CAM to discover the abstraction graph $G$, which is
then filtered to remove the nodes from which error nodes are not
reachable. In all our experiments we used $1$-relational modeling to
create the transition system from $G$. This was determined to be a
good trade-off between longer simulations and increase in precision,
with respect to the mentioned benchmarks.

Using the BMC, we checked for the given safety property. If a concrete
trace was obtained, it was further checked for reproducibility by
sampling and simulating its `neighborhood' with the $\simulate$
function. We define `neighborhood' as the abstract states
corresponding to the returned concrete trace.  Specifically, $100$
samples were uniformly randomly chosen and simulated and tested for
error traces. This procedure can also be extended to obtaining
different discrete sequences or discrete trace sequences from the
model checker by requesting distinct counter-examples.
